---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pinsManifest

<!-- badges: start -->
[![R-CMD-check](https://github.com/ijlyttle/pinsManifest/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ijlyttle/pinsManifest/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of pinsManifest is to help with a particular use-case for [pins]():

 - you create a board using `pins::board_folder()`
 - you serve the board using `pins::board_url()`
 
The mechanism is to make a *manifest* file of pins used to create a `pins::board_url()`. 

## Installation

You can install the development version of pinsManifest from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ijlyttle/pinsManifest")
```

## Example

```{r}
library("pinsManifest")
```

### Writing a folder-board

Let's say you have a `pins::board_folder()` that you want to serve as a website, perhaps using GitHub.
You can write a manifest file for the pins using `pin_write_manifest()`:

``` r
board <- pins::board_folder("/some/path")

# add/update pins

pin_write_manifest(board)
```

```
#> Manifest file written to `/some/path/pins.txt`
```

This writes a manifest file, `pins.txt` to root directory of your board.
It stores the names of your pins and the names of each version of each pin.

Note: `pin_write_manifest()` supports only boards created using `pins::board_folder()`.

### Reading a URL-board

To create a `pins::board_url()`, you need a named character-vector where:

   - names are names of pins
   - values are the URLs that point to a version-directory
   
The problem is that the names of version directories are, by design, hard to predict and manage manually.

This is where a manifest file, `pins.txt` can help. 
When you call `board_url_manifest()`, it downloads `pins.txt`, then parses it to provide information to build a `pins::board_url()`.

A demonstration board is provided using `url_demo_manifest()`:

```{r}
board_demo <- board_url_manifest(url_demo_manifest())

pins::pin_list(board_demo)
pins::pin_meta(board_demo, "mtcars-json")
```

### Behind the scenes

The function `manifest_latest()`:

  - takes a `url` describing the root directory of a board
  - downloads and parses the `pins.txt` file at the root
  - returns a named character vector where:
    - names are names of pins
    - values are URLs to directory for the latest version for each pin

The return value can be used to build a `pins::board_url()`:
    
```{r}
manifest_latest(url_demo_manifest())
```
